Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-31 write_up/parameter_tables.tex
Revised manuscript

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population and recruitment
		dynamics sub-modules.}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Rate of fishing mortality in cell $c$
		on day $d$ & $d^{-1}$ \\
		$M_{c,d}$ & Rate of natural mortality in cell $c$
		on day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the number of fish recruited in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate (Beverton Holt)
		or maximum productivity per spawner (Ricker) & number fish  \\
		$\beta$ & the stock size required to produce half the maximum rate
		of recruitment (Beverton Holt) or density dependent reduction
		in productivity per capita of SSB & number fish \\
		\bottomrule
		\end{tabular}
\end{table}

@@

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module.}
	\label{tab:fleet_dyn}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro.kg$^{-1}$ \\
		Le & Step length for vessel & - \\
		$Br$ & Bearing & degrees \\
		$k$ & Concentration parameter for von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting.}
\begin{tabular}{ p{4cm } p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences & pop 2/4 & pop 1/3 & - & pop 4 & pop
	2/3 \\
	\hline
	Price $Pr_{p}1$ = 100 & & & & & \\
	Price $Pr_{p}2$ = 200 & & & & & \\
	Price $Pr_{p}3$ = 350 & & & & & \\
	Price $Pr_{p}4$ = 600 & & & & & \\
	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
	step function $\beta_3$, the landings value $nth$ quantile &
	90 & 90 & 85 & 90 & 80 \\
	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
	Past Knowledge = TRUE & & & & & \\
	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

>>>>

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population and recruitment
		dynamics sub-modules.}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Ford's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Rate of fishing mortality in cell $c$
		on day $d$ & $d^{-1}$ \\
		$M_{c,d}$ & Rate of natural mortality in cell $c$
		on day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the number of fish recruited in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate (Beverton Holt)
		or maximum productivity per spawner (Ricker) & number fish  \\
		$\beta$ & the stock size required to produce half the maximum rate
		of recruitment (Beverton Holt) or density dependent reduction
		in productivity per capita of SSB & number fish \\
		\bottomrule
		\end{tabular}
\end{table}

@@

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module.}
	\label{tab:fleet_dyn}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		$Rev$ & Revenue from fishing tow & \euro \\
		$RefRev$ & Reference revenue for determining the step function
		& \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro.kg$^{-1}$ \\
		Le & Step length for vessel & - \\
		$Br$ & Bearing & degrees \\
		$k$ & Concentration parameter for von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting.}
\begin{tabular}{ p{4cm } p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences & pop 2/4 & pop 1/3 & - & pop 4 & pop
	2/3 \\
	\hline
	Price $Pr_{p}1$ = 100 & & & & & \\
	Price $Pr_{p}2$ = 200 & & & & & \\
	Price $Pr_{p}3$ = 350 & & & & & \\
	Price $Pr_{p}4$ = 600 & & & & & \\
	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	$\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	$\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
	$\beta_3$, the landings value $nth$ quantile &
	90 & 90 & 85 & 90 & 80 \\
	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
	Past Knowledge = TRUE & & & & & \\
	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}
